Appendix

### 2020-04-21 appendix/appendixV5.Rmd
Saving plots

# Needed packages
pkgs <- c('tidyverse', 'meta', 'metafor', 'readxl',
          'dmetar', 'knitr', 'gridGraphics', 'gridExtra','ggpubr','kableExtra')

@@

f1 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(color = "black") +
  # Error Bars
  geom_errorbarh(height = 0.1) +
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="black", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank())

f1
```

@@

f2 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(color = "black") +
  # Error Bars
  geom_errorbarh(height = 0.1) +
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="black", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank()) 
f2

@@

f3
```

@@

f4
```

@@

f5
```

@@

f6
```

@@

f7
```

@@

@@

f8

@@

f9 <- mod2 %>%
  ggplot(aes(y = reorder(studlab,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(color = "black") +
  # Error Bars
  geom_errorbarh(height = 0.1) +
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Vertical dashed line
  geom_vline(xintercept=0, color="black", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank()) 
f9
```

@@

f10
```

@@

f11
```

@@

f12
```

@@

f13
```

@@

f14
```

@@

grid.arrange(f8, f9, f11, 
             f10,f12, f13,
             f14,
             ncol = 2,
             nrow = 4)
#library(ggplot2)

>>>>

# Needed packages
pkgs <- c('tidyverse', 'meta', 'metafor', 'readxl',
          'dmetar', 'knitr', 'gridGraphics', 'gridExtra','ggpubr','kableExtra','magick')

@@

f1 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(color = "black") +
  # Error Bars
  geom_errorbarh(height = 0.1) +
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="black", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank()) 
f1
ggsave("./plots/f1.png", width = 20, height = 10, units = "cm")

@@

f2 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(color = "black") +
  # Error Bars
  geom_errorbarh(height = 0.1) +
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="black", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank()) 
f2
ggsave("./plots/f2.png", width = 20, height = 10, units = "cm")
```

@@

f3
ggsave("./plots/f3.png", width = 20, height = 10, units = "cm")
```

@@

f4
ggsave("./plots/f4.png", width = 20, height = 10, units = "cm")
```

@@

f5
ggsave("./plots/f5.png", width = 20, height = 10, units = "cm")
```

@@

f6
ggsave("./plots/f6.png", width = 20, height = 10, units = "cm")
```

@@

f7
ggsave("./plots/f7.png", width = 20, height = 10, units = "cm")
```

@@

#f1 + rotate()

@@

f8
ggsave("./plots/f8.png", width = 20, height = 10, units = "cm")
```

@@

f9 <- mod2 %>%
  ggplot(aes(y = reorder(studlab,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(color = "black") +
  # Error Bars
  geom_errorbarh(height = 0.1) +
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Vertical dashed line
  geom_vline(xintercept=0, color="black", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank()) 
f9
ggsave("./plots/f9.png", width = 20, height = 10, units = "cm")
```

@@

f10
ggsave("./plots/f10.png", width = 20, height = 10, units = "cm")
```

@@

f11
ggsave("./plots/f11.png", width = 20, height = 10, units = "cm")
```

@@

f12
ggsave("./plots/f12.png", width = 20, height = 10, units = "cm")
```

@@

f13
ggsave("./plots/f13.png", width = 20, height = 10, units = "cm")
```

@@

f14
ggsave("./plots/f14.png", width = 20, height = 10, units = "cm")
```

@@

blank = ggplot() + 
  geom_blank() +
  theme_minimal()
blank
ggsave("./plots/zz_blank.png", width = 20, height = 10, units = "cm")

plots = list.files(path = "./plots/", pattern = "*.png") %>%
  map(~{
    image_rotate(image_read(path = paste0("./plots/", .x)), 270)
  })

p_1 = image_append(c(plots[[3]], plots[[2]], plots[[1]]), stack = T)
p_2 = image_append(c(plots[[6]], plots[[5]], plots[[4]]), stack = T)
p_3 = image_append(c(plots[[15]],plots[[7]],plots[[15]]), stack = T)
p_full = image_append(c(p_1, p_2, p_3))
p_full

#p_full

#ggpubr::ggarrange(plots[[1]],plots[[2]],
#                  plots[[3]],plots[[4]],
#                  plots[[5]],plots[[6]],
#                  plots[[7]],
#                  nrow = 4, ncol = 2
#                  )
